Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-21 authors.tex
authors: Modify my name to remove Turkish chars
I'm generally using a non-Turkish version of my last name.

\textbf{Ozan Çağlayan}$^{7\ddagger}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Matt Hall}$^{15\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},

>>>>

\textbf{Ozan Caglayan}$^{7\ddagger}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Matt G. Hall}$^{15\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
